Tobacco

### 2023-02-15 docsrc/documentation/notebooks/housing.Rmd
get all current module templates with better formatting in taskbar.

# Housing Quality

@@

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

## Methods

@@

## Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

## References

>>>>

## Housing Quality

@@

```{r housing_setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

### Methods

@@

```{r housing_barchart, echo=FALSE}
print(table(real_data$housing_quality))
discrete_barplot("housing_quality")
```

### Data

@@

```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("../../../data/transitions/test/housing_clm_2018_2019.rds", "housing_quality_next")
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```

### References

### 2023-02-15 docsrc/documentation/notebooks/labour.Rmd

```{r labour_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds") #e.g. ../../../data/transitions/test/housing_clm_2018_2019.rds
nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state)')
```

>>>>

```{r labour_output, echo=FALSE}
options(width=120)
nnet_output("../../../data/transitions/test/labour_nnet_2018_2019.rds")
nnet_confusion_matrix("../../../data/transitions/test/labour_nnet_2018_2019.rds", mode='multinom', 'factor(labour_state_next)')
```

### 2023-02-15 docsrc/documentation/notebooks/tobacco.Rmd

---
title: "Tobacco Transition Module"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

# Tobacco

Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson].

@@

## Methods

  What methods are used? Justification due to output data type. explanation of model output.

## Data

@@

## Results

  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
```

## References

>>>>

---
title: "Tobacco"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

## Tobacco

Number of cigarettes consumed is an indicator of several mental illnesses including anxiety [@lawrence2010anxiety].

@@

### Data

@@

```{r tobacco_data}
counts_density('ncigs')
```

### Methods

The number of zero inflated values is higher than expected for a count distribution such as a poisson distribution. This inflation occurs naturally as a large proportion (over 50\%) of the population do not smoke. There are two sources of cigarette consumption that can be modelled using zero inflated models. In this case a zero-inflated poisson (ZIP) is used. Two models are fitted simulatenously. One is a logistic regression that estimates whether a person smokes cigarettes or not. This provides a simple probability of smoking or not. The second is a poisson counts model estimating the number of cigarettes consumed.

### Data

Two set of variables are needed for the logistic and poisson parts of the ZIP model respectively.

Variables that predict how much a person smokes.

age. persons age. generally older people and very young smoke. 
SF_12. wellbeing estimates number of cigarettes smoked.
labour_state. whether a person is employed or not.
ethnicity. certain ethnicities more likely to smoke cigarettes. 
education_state. highest qualification.
job_sec job quality
hh_income household income
ncigs previous number consumed.

Variables that predict whether a person smokes

ethnicity. certain ethnicities more likely to smoke cigarettes. 
labour_state. whether a person is employed or not.
age
SF_12. wellbeing estimates number of cigarettes smoked.
ncigs previous number consumed.

### Results

Almost all coefficients significant. Particularly prevous consumption of cigarettes. Good estimation of the number of non-smokers in the population at around 55\%. Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes.

```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("../../../data/transitions/test/tobacco_zip_2018_2019.rds")
zip_density("../../../data/transitions/test/tobacco_zip_2018_2019.rds", 'ncigs_next')
```

### References
